\chapter{Team Meeting Minutes}
\minutesessentials{19}{2013-12-03}{15:00-15:25}{PKI 201C}{Present}{Present}{Present}{Present}
\minutesdetails
{
	\item Receive feedback from Detloff on the Project Plan.
	\item Determine which modifications to the report will be required.
	\item Review the \gls{pssc} with Detloff to improve upon the engineering requirements.
	\item Schedule time to meet for questions regarding the project proposal.}
{
	\item The critical path will be marked on the \gls{aon}.
	\item The milestones will be explained better for easier understanding. 
	\item Top level of WBS will be the complete project.
	\item PSSCs need to cover the objectives.
	\item A meeting for questions about the Project Proposal would be held on Thursday December 5th at 16:00.
}

\minutesessentials{20}{2013-12-05}{14:00-14:45}{PKI 330}{Present}{Present}{Present}{Present}
\minutesdetails
{
	\item Developed agenda for meeting with Professor Detloff about the Project Proposal}
{
	\item Team would ask for more specifics on each section.
	\item Team would ask to review the PSSCs.
}

\minutesessentials{21}{2013-12-05}{16:00-16:35}{PKI 201C}{Present}{Present}{Present}{Present}
\minutesdetails
{
	\item Questions about the Project Proposal were asked. 
	\item Specifics for each section were reviewed.
	\item PSSCs were reviewed.}
{
	\item Specifics about each section were given.
	\item Team was advised on how to update their PSSCs.
}

\minutesessentials{22}{2013-12-10}{19:20-22:00}{PKI 330}{Present}{Present}{Present}{Present}
\minutesdetails
{
	\item Meet to finish up the Project Proposal}
{
	\item Paper was finished.
}

\signatures