\chapter{Economic Analysis}
%should be societal/global?
\section{Economic Analysis}
The \gls{cnc} is one of few growing hardware based enterprises in the modern technology market.
In allowing manufacturers greater control over the production process, a wider variety of goods can be produced with limited machinery.
This in turn means that fewer capital resources are required in manufacturing, and production centers can be localized.
Consumers will benifit greatly from the "highly flexible, small-scale manufacturing" provided by the \gls{cnc}.

The \gls{ceenc} brings this technology to an even broader audience, in allowing consumers themselves to produce goods from raw materials.
Persons may circumvent the supply chain entirely, by uploading and milling custom objects on the device.
For example, in past years obtaining a differential retainer clip for a 1987 Nissan Hardbody Pickup Truck may have involved a trip to the store, and an order from a centralized warehouse.
This measure could be circumvented entirely however, if the store were to provide \gls{cnc} services, and manufacture the item on the spot. 
Distribution can be made even simpler by making it a household device.

Procuring parts from washing machine load couplers to blender bases with the \gls{ceenc} is as simple as uploading a file.
This in turn increases the overal product lifespan.
While this project has been completed on strictly non-profit grounds, the economic implications for the technology as a whole is staggering.

\section{Environmental Analysis}
Environmental impact is the area in which the \gls{ceenc} provides quantifiable benefit. 
Current \gls{cnc} controller implementations are large, and generate a great deal of heat. 
The \gls{ceenc} uses modern drivers to greatly increase efficiency and reduce power consumption. 
Computational components have also been reduced, and are significantly better suited for controlling these devices than full fledged PC towers. 

Combination of the factors above reduces the materials required in construction of the \gls{ceenc} by a factor of 10. 
Although limited considerations have been made pertaining to the ROHS certification of the components involved, it is safe to say that in removal of the PC tower from the control loop, it will most certainly prove to be a net positive for the environment. 
Optimization of power consumption has a twofold impact, not only in conservation of electricity, but in minimization of materials required for heat sinking and structure.

Finally, as mentioned in the Economic Analysis, \gls{cnc} technology will impact supply and distribution chains worldwide.
While mass manufacturing will maintain its place as a method by which goods can be produced cheaply and effectively, the offset in shipping costs for localized manufacture will see less freight shipped overall.

\section{Sustainability}
The highly modular construction of the \gls{ceenc} will greatly increase its projected lifespan.
Targeted to audiences in the fields of science and engineering, the construction is such that they will be able to repair or repurpose components as they see fit.
In seperation of the computational, control, and driver components, persons are able to integrate any section of the system with existing devices.
For example, the control card is capable of controlling not only the custom driver card, but any number of \gls{cnc} utilizing the standard interface as well.
The same works in reverse for the driver card, and should the end user see fit, the computational control can be replaced by any system with an SPI interface.

For projected long term growth of the \gls{ceenc} brand, the technology utilized in its design is expected to remain relevant for another 5 to 10 years.
Many current \gls{cnc} systems on the market today still utilize chipsets devised in the late 80's like the L298. 
The \gls{ceenc} has made use of modern motor drivers and microcontrollers with high industry backing.
Until entire \gls{cnc} systems on a chip go into manufacture, the \gls{ceenc} will remain an optimal means by which consumers can control their \gls{cnc} devices.
 
\section{Manufacturability}
Component selection for the \gls{ceenc} was centered around ease of diagnosis, repair, and human assembly.
This in turn puts the system as it stands at a disadvantage for mass production, but inhibited the growth of 3214 gray hairs between its 4 designers.
Should the device go into production, components will be selected based on size, cost, and package. 
The DRV8825 breakout boards will be placed directly on the device, and as many through-hole components as possible will be replaced with surface mount equivalents.
The \gls{pi} will also be eliminated from the system, and the entire assembly placed on a single board.

While operational environment concerns were largely ignored for the prototyping of this device, its use in high dust conditions delegates the need for conformal coating on all surfaces.
Potting compound should also be applied to reduce damages incurred from excessive vibration.
Finally, the enclosure should be made to manage airflow in a manner that mitigates the migration of mites into the membrane of its heat sinks.
 
\section{Ethical}
Legal concerns pertaining to “warning label placement” are greatly simplified by the limited scope of the CEEN-C. 
Safety concerns will arise largely from the machinery which the device is to drive, and as such are specific to its implementation. 
With no lethal voltages, or hazardous RF interference produced by the components, it is then the sole duty of the CEEN-C to power off when commanded, and not start on fire. 
These have both been explicitly outlined by the PSSC’s, and are a standard feature in most electronics of this type.

More pertinent to the societal impact of this project, is the management of source documentation and intellectual property. 
With much of the design drawing from the open source community, it is important that the information generated by the exercise be reciprocated by its participants. 
In this manner, the world can be positively impacted in the creation of new solutions to common problems. 
