\chapter{Introduction}
1. Orient the reader to the topic

WHAT DOES THIS MEAN?
The CeeNC is a web enabled \gls{cnc} interface designed with students and hobbyists in mind. 
While most modern \gls{cnc} systems are expensive and large, the CeeNC is an affordable and compact device. 
The device can also be configured for multiple setups, like a linear \gls{cnc}, a Delta Robot, or a 3D printer. 
The web interface also improves upon current \gls{cnc} computer interfaces, which are not user friendly, and allows a user to use their device from anywhere on the network.


2. Explain the particular problem that is addressed in the report.	
In most cases, owning a \gls{cnc} requires a large monetary investment, along with a sizable area to keep it in. 
This makes it hard for students and hobbyists, along with some companies, to be able to have their own \gls{cnc}.
A personal \gls{cnc} can cut down on project development time.
The user interfaces for \gls{cnc} control that are currently availble are not known to be user friendly.

3. State what your project needs to accomplish

The purpose of the CeeNC is to create a \gls{cnc} interface, capable of receiving standardized G-code through \gls{tcpip}, processing the G-code, and driving motors and \gls{gpio} according to the G-code. 
G-code is a standard \gls{cnc} programming language, but is more complicated than accepting individual commands to move the motors.


4. Describe the organization and structure of the report.

DO I JUST TALK ABOUT ALL THE FOLLOWING SECTIONS?
The following will discuss the need for the product, the process used to design solutions, the solutions that were implemented and how they will work, and how the solutions may affect the world.
Lastly, recommendations will be suggested on how the project can move forward.
